Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-24 sattose/paper.tex
Referring to the tables

Running our clone detection script, CloneRefactor, over this corpus gives the following results:

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.}
  \bigskip
\begin{tabular}{|l|l|}
\hline
Amount of projects                                                                                      & 3.848      \\ \hline
Amount of lines                                                                                         & 8.284.140  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8.163.429  \\ \hline
Amount of statements/declarations                                                                       & 6.863.725  \\ \hline
Amount of tokens                                                                                        & 66.964.270 \\ \hline
Amount of lines cloned                                                                                  & 1.341.094  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815.799    \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747.993    \\ \hline
Amount of tokens cloned                                                                                 & 9.800.819  \\ \hline
Amount of clone classes                                                                                 & 34.367     \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\subsubsection{Our measurements}
We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
\begin{itemize}
  \item We consider clone classes rather than clone pairs.
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
\end{itemize}

The table below shows our results.

\begin{table}[H]
  \begin{center}
  \caption{Clone relations}
  \bigskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13.537           & 39,39               \\ \hline
Same Class          & 8.341            & 24,27               \\ \hline
Sibling            & 5.978            & 17,39               \\ \hline
Same Method         & 2.456            & 7,15                \\ \hline
External Superclass & 2.402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, their source for this information, uses a very questionable techique of measuring (human copy-paste behaviour with a small sample-size). We set out to test this for ourselves on our corpus, and got the following results:

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
Method Level       & 19.818           & 57,68               \\ \hline
Class Level        & 13.259           & 38,59               \\ \hline
Constructor Level  & 1.099            & 3,20                \\ \hline
Interface Level    & 110              & 0,32                \\ \hline
Enum Level         & 74               & 0,22                \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents}
  \bigskip
\begin{tabular}{|l|l|l|}
  \hline
  \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
  Partial Method                                                           & 19.264          & 56,07               \\ \hline
  Several Methods                                                          & 9.076           & 26,41               \\ \hline
  Includes Constructor                                                     & 1.528           & 4,45                \\ \hline
  Includes Field                                                           & 1.149           & 3,34                \\ \hline
  Partial Constructor                                                      & 1.098           & 3,20                \\ \hline
  Only Fields                                                              & 565             & 1,64                \\ \hline
  Full Method                                                              & 554             & 1,61                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1,30                \\ \hline
  Other                                                                    & 369             & 1,07                \\ \hline
  Full Class                                                               & 192             & 0,56                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0,15                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0,14                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0,03                \\ \hline
  Full Interface                                                           & 6               & 0,02                \\ \hline
  Full Enumeration                                                         & 4               & 0,01                \\ \hline
  Full Constructor                                                         & 1               & 0,00                \\ \hline
\end{tabular}
\end{center}
\end{table}
%TODO: Finish text and add measurements.

>>>>

Running our clone detection script, CloneRefactor, over this corpus gives the results displayed in table \ref{table:general}.

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
  \bigskip
\begin{tabular}{|l|l|}
\hline
Amount of projects                                                                                      & 3.848      \\ \hline
Amount of lines                                                                                         & 8.284.140  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments, etc.)\end{tabular}        & 8.163.429  \\ \hline
Amount of statements/declarations                                                                       & 6.863.725  \\ \hline
Amount of tokens                                                                                        & 66.964.270 \\ \hline
Amount of lines cloned                                                                                  & 1.341.094  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments, etc.)\end{tabular} & 815.799    \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of statements/declarations\\ cloned\end{tabular}                      & 747.993    \\ \hline
Amount of tokens cloned                                                                                 & 9.800.819  \\ \hline
Amount of clone classes                                                                                 & 34.367     \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\subsubsection{Our measurements}
We have recreated table 3 of Fontana et al \cite{fontana2015duplicated}, but with the following differences in our setup:
\begin{itemize}
  \item We consider clone classes rather than clone pairs.
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality).
\end{itemize}

Table \ref{table:relations} contains our results regarding the relations between clone instances.

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \bigskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13.537           & 39,39               \\ \hline
Same Class          & 8.341            & 24,27               \\ \hline
Sibling            & 5.978            & 17,39               \\ \hline
Same Method         & 2.456            & 7,15                \\ \hline
External Superclass & 2.402            & 6,99                \\ \hline
First Cousin        & 695             & 2,02                \\ \hline
Superclass         & 488             & 1,42                \\ \hline
Common Hierarchy    & 442             & 1,29                \\ \hline
Ancestor           & 28              & 0,08               \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

A paper by Lozano et al \cite{lozano2007evaluating} discusses the harmfulness of cloning. In this paper the author argues that 98\% are produced at method-level. However, their source for this information, uses a very questionable techique of measuring (human copy-paste behaviour with a small sample-size). We set out to test this for ourselves on the corpus of Java projects which we used for all our measurements. The results for the clone instance locations are shown in table \ref{table:locations}.

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations} \label{table:locations}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
Method Level       & 19.818           & 57,68               \\ \hline
Class Level        & 13.259           & 38,59               \\ \hline
Constructor Level  & 1.099            & 3,20                \\ \hline
Interface Level    & 110              & 0,32                \\ \hline
Enum Level         & 74               & 0,22                \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

The results for these categories are displayed are displayed in table \ref{table:contents}.

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents} \label{table:contents}
  \bigskip
\begin{tabular}{|l|l|l|}
  \hline
  \textbf{Contents}                                                        & \textbf{Amount} & \textbf{Percentage} \\ \hline
  Partial Method                                                           & 19.264          & 56,07               \\ \hline
  Several Methods                                                          & 9.076           & 26,41               \\ \hline
  Includes Constructor                                                     & 1.528           & 4,45                \\ \hline
  Includes Field                                                           & 1.149           & 3,34                \\ \hline
  Partial Constructor                                                      & 1.098           & 3,20                \\ \hline
  Only Fields                                                              & 565             & 1,64                \\ \hline
  Full Method                                                              & 554             & 1,61                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Class\\ Declaration\end{tabular}     & 445             & 1,30                \\ \hline
  Other                                                                    & 369             & 1,07                \\ \hline
  Full Class                                                               & 192             & 0,56                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Constant\end{tabular}         & 52              & 0,15                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Enum\\ Declaration\end{tabular}      & 47              & 0,14                \\ \hline
  \begin{tabular}[c]{@{}l@{}}Includes Interface\\ Declaration\end{tabular} & 10              & 0,03                \\ \hline
  Full Interface                                                           & 6               & 0,02                \\ \hline
  Full Enumeration                                                         & 4               & 0,01                \\ \hline
  Full Constructor                                                         & 1               & 0,00                \\ \hline
\end{tabular}
\end{center}
\end{table}
%TODO: Finish text and add measurements.
